%!TEX program = xelatex
\documentclass[a4paper]{cv}
\begin{document}
\pagecolor{bg}
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------
\begin{center}
\name{Théo Lemaire}\\
\vspace{5pt}
\tag{Bioengineer \& Versatile Programmer}\\
\address{Rue des Maraîchers 46}{1205 Genève}{CH}\ \ \ \email{theo.lemaire1@gmail.com}\ \ \ \mobilephone{+41 79 629 39 05}\ \ \ \linkedin{https://ch.linkedin.com/in/theolemaire}{theolemaire}
\end{center}
%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------
\hspaceleft\begin{minipage}[t]{0.6\textwidth}

\section{\texorpdfstring{\faBriefcase}\ \ Experience}\sectionline

\runsubsection{Ph.D. in Neuroengineering}
\descript{| \href{http:// tne.epfl.ch/}{TNE Lab, EPFL}}
\timeplace{Apr 2016 - Mar 2020}{Campus Biotech, Geneva, CH}
Development of a multiscale modeling framework to understand and optimize Ultrasound Neuromodulation.
\sectionspace

\runsubsection{Ski \& Snowboard Instructor}
\descript{| \href{http://www.esf.net}{Ecole du Ski Français}}
\timeplace{Jan 2013 - Present}{Monts Jura, FR}
5-years experience with private and collective lessons to both adults and kids, from beginners to competitors. State diploma training currently underway.
\sectionspace

\runsubsection{Mathematics Teacher}
\descript{| \href{http://www.jda-gex.org/college}{Institution Jeanne d'Arc}}
\timeplace{Nov 2015 - Dec 2015}{Gex, FR}
1-month experience as a middle school mathematics teacher (3 classes). Learned to build up my authority and to create a learning dynamics inside a class.
\sectionspace

\runsubsection{Software Engineering Intern}
\descript{| \href{http://www.zenithtechnologies.com/}{Zenith Technologies}}
\timeplace{Apr 2013 – Aug 2013}{Cork, IRL}
Designed a C++ application to extract relevant data from a \href{http://www3.emersonprocess.com/deltav/version13/}{\emph{DeltaV}} database and provide team leaders with a comprehensive overview of their project's evolution. Created VBA scripts used by collaborators to generate documentation.
\sectionspace

\runsubsection{Kinesiology Lab Intern}
\descript{| \href{http://www.hug-ge.ch/chirurgie-orthopedique-traumatologie-appareil/laboratoire-cinesiologie}{Geneva University Hospitals}}
\timeplace{Aug 2012 - Jan 2013}{Geneva, CH}
Developed a MATLAB framework (GUI, processing \& graphing tools, interaction with database, PDF generation) to analyse biomechanical data from clinical examinations. Used by lab members for daily reporting and scientific publications.\sectionspace

\section{\texorpdfstring{\faClipboard} \ \ Academic Projects}\sectionline

\runsubsection{Master’s thesis in Neuroprosthetics}
\descript{| \href{http://tne.epfl.ch/}{TNE Lab, EPFL}}
Computer modeling of nerve-electrode interfaces with the \href{http://www.zurichmedtech.com/sim4life/}{\emph{Sim4Life}} simulation platform to improve the development of upper-limb neuroprostheses.
\sectionspace

\runsubsection{Project in Biorobotics}
\descript{| \href{http://biorob.epfl.ch/}{BIOROB Lab, EPFL}}
Developed a computer-vision tool on the \href{https://www.cyberbotics.com/overview}{\emph{Webots}} simulator allowing a differential wheeled robot to detect and navigate through colored rectangular frames.
\sectionspace

\runsubsection{Project in Digital Humanities}
\descript{| \href{http://dhlab.epfl.ch/}{DH Lab, EPFL}}
Numerical simulations of a novel spatio-temporal epidemics model to study the propagation of the Plague in the city of Venice during Middle-Age.\weblink{http://veniceatlas.epfl.ch/atlas/experience/simulation/the-plague/}{Venice Atlas}
\sectionspace

\section{\texorpdfstring{\faWrench}\ \ Technical Skills}\sectionline

% \mlovalbox{\textbf{C++} (\approx \emph{3000 hrs}): OOP \tbl{} IO streams \tbl{} Parsing \& serialization \tbl{} XML-quering \tbl{} Multithreading with \href{https://www.boost.org/}\emph{Boost} \tbl{} GUIs with \href{https://www.wxwidgets.org/}{\emph{wxWidgets}} \tbl{} 3D graphics in \href{https://www.opengl.org/}{\emph{OpenGL}}}
% \mlovalbox{\textbf{MATLAB} (\approx \emph{2000 hrs}): Scientific computing \tbl{} Digital signal processing \tbl{} Machine learning \tbl Interaction with SQL databases \tbl{} Complex GUIs}
% \mlovalbox{\textbf{Python} (\approx \emph{3000 hrs}): Scientific computing (\emph{NumPy}, \emph{SciPy}) \tbl{} Integration of stiff ODE systems \tbl{} GUIs with \emph{Tkinter} \tbl{} 3D animations with \emph{VPython} \tbl{} IO streams to Excel files \tbl{} Automatic emailing \tbl{} API interaction \tbl{} Documentation with \emph{Sphinx}}
% \mlovalbox{\textbf{Front-End Web} (\approx \emph{200 hrs}): Responsive web pages with \emph{Javascript}, \emph{HTML5}, \emph{CSS3} \& \href{http://getbootstrap.com/}{\emph{Bootstrap}} \tbl{} Charts \& animations with \href{https://d3js.org}{\emph{D3JS}}}
% \ovalbox{\textbf{MS Office \& VBA}} \ \ovalbox{\textbf{LaTeX}} \ \ovalbox{\textbf{Illustrator}} \ \ovalbox{\textbf{LabVIEW}} \ \ovalbox{\textbf{Finite Element Modeling}}

\wheelchart{1.5cm}{0.5cm}{%
  6/12em/blue3/{\cvskill{matlab.pdf}{Matlab}\\ Scientific computing\\ Machine learning \tbl{} GUIs\\ Database interaction},
  6/12em/blue2/{\cvskill{python.pdf}{Python}\\ Scientific computing\\ GUIs \tbl{} 3D animations \\ Finite Element Models\\ NEURON},
  2/12em/blue4/{\cvskill{vba.pdf}{Visual Basic}\\ Macros for Word \& Excel},
  6/12em/blue1/{\cvskill{gears.pdf}{\CC}\\ Object-oriented progr.\\ Multithreading\\ GUIs \tbl{} 3D graphics},
  3/12em/blue5/{\cvskill{frontend.pdf}{Front-End}\\ \emph{Javascript} \tbl{} \emph{HTML5} \tbl{} \emph{CSS3}\\ \emph{Bootstrap} \tbl{} \emph{D3JS}}
}

\vspace{10pt}
\centering{\cvskill{msword.pdf}{MS Office} \tbl{} \cvskill{blank.pdf}{\hspace{-5pt}\LaTeX} \tbl{} \cvskill{illustrator.pdf}{Illustrator} \tbl{} \cvskill{labview.pdf}{LabVIEW} \tbl{} \cvskill{git.pdf}{Git}}

\end{minipage}
\hsepcol
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.33\textwidth}

\section{\texorpdfstring{\faGraduationCap} \ \ Education}\sectionline

\subsection{MSc in Bioengineering}
\subsection{Minor in Neuroprosthetics}
\descript{\href{http://www.epfl.ch}{EPF Lausanne}}
\timeplace{Sept 2013 - Sept 2015}{Lausanne, CH}
GPA: 5.34 / 6.0
\sectionspace

\subsection{BSc in Life Sciences \& Technologies}
\descript{\href{http://www.epfl.ch}{EPF Lausanne}}
\timeplace{Sept 2009 -July 2012}{Lausanne, CH}
GPA: 4.92 / 6.0
\sectionspace

\subsection{Scientific baccalaureate}
\descript{Lycée Int. Ferney Voltaire}
\timeplace{Sept 2006 - July 2009}{Ferney, FR}
GPA: 18.71 / 20.0
\sectionspace

\section{\texorpdfstring{\faBook} \ \ Coursework}\sectionline

\subsection{Graduate}
Sensorimotor neuroprosthetics\\
Flexible bioelectronics\\
Image processing \tbl{} Machine learning\\
Dynamical systems \tbl{} Biomechanics\\
Gait analysis \& modeling\\
Computational motor control\\
Bioinformatics \tbl{} Systems biology\\
Digital humanities
\sectionspace

\subsection{Undergraduate}
Analysis \tbl{} Algebra \tbl{} Physics\\
Chemistry \tbl{} Organic chemistry\\
Cellular biology \tbl{} Molecular biology\\
Numerical analysis \tbl{} Statistics\\
Electronics \tbl{} Signal processing\\
Programming (C | C++ | Matlab)\\
Development biology \tbl{} Microbiology\\
Physiology \tbl{} Genetics \tbl{} Genomics\\
Fluid dynamics \tbl{} Transport phenomena\\
Biothermodynamics \tbl{} Neuroscience
\sectionspace

\section{\texorpdfstring{\faComments} \ \ Languages}\sectionline

\noindent\begin{tabular}{@{}ll}
\textbf{French} & \fivestars \\
\textbf{English} & \fourstarshalf \\
\textbf{German} & \threestarshalf \\
\textbf{Russian} & \onestar \\
\end{tabular}
\sectionspace

\section{\texorpdfstring{\faHeart}\ \ Hobbies}\sectionline

\noindent\begin{tabular}{@{}c@{}c@{}c@{}c@{}}
\glyph{atom.pdf}{Science} & \glyph{taekwondo.pdf}{Taekwondo} & \glyph{football.pdf}{Football} & \glyph{television.pdf}{TV Shows}\\
\glyph{skiing.pdf}{Skiing} & \glyph{mountains.pdf}{Hiking} & \glyph{cycling.pdf}{Cycling} & \glyph{travel.pdf}{Travels}
\end{tabular}

\end{minipage}
\end{document}